### 2018-04-29 Paper/sense.tex
..

As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD
are dependent on the choice of the inter-atomic potential as well as values associated with
the individual potential parameters. In the case of silicon, the Stillinger-Weber inter-atomic potential
has been used for a wide variety of 
systems~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein).
However, according to Stillinger and Weber, the set of nominal
values as provided below in Table~2 is based on a constrained search in the 7D parameter space
to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.

@@

It is noteworthy that the underlying analysis which lead to these estimates of the nominal values did not
account for the presence of uncertainty due to
measurement error, noise inherent in MD predictions, inadequacies pertaining to the potential function,
and parametric uncertainties. It is therefore likely that the proposed nominal estimates could be 
improved depending upon the application. Hence, it is critical to understand the effects of variability in
SW potential parameters on bulk thermal conductivity predictions using NEMD. For this purpose, a possible
approach could involve a global sensitivity analysis of NEMD predictions on the SW potential parameters 
by estimating the so-called Sobol indices~\cite{Sobol:2001}. However, obtaining converged estimates of
Sobol indices typically requires tens of thousands of model evaluations. Since NEMD is compute-intensive,
estimating the Sobol indices directly would be impractical. Instead, we adopt a novel strategy that
aims to determine relative importance of the SW potential parameters based on derivative-based global 
sensitivity measures (DGSM)~\cite{Sobol:2010}. It is observed that for a given application, it might be possible to 
converge to the upper bound on
Sobol index with only a few iterations~($\mathcal{O}(10^{1})$). 
In that case, estimates of the upper bound could be used in lieu of the
Sobol indices to determine relative importance of the parameters and hence reduce the associated computational
effort by several order of magnitude. The upper bound on 
Sobol total effect index\footnote{Sobol total effect index is a measure of the contribution of a 
parameter to the variance of the observable while contribution from other parameters may or may not be 0.}
($\mathcal{T}_i$) can be expressed in terms of DGSM~($\mu_i$), the Poincar\' e 
constant~($\mathcal{C}_i$), and the total variance of the observed
quantity~($V$)~\cite{Lamboni:2013,Roustant:2014} as follows:

@@

\noindent The derivative-based sensitivity measure, $\mu_i$ for a given parameter, $\theta_i$ is
defined as an expectation
of the derivative of the observable ($G(\bm{\theta})$) with respect to that parameter:

@@

We aim to compute the derivative-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
Sobol total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
associated with each parameter and estimate the partial derivatives in Eq.~\ref{eq:mu} using finite difference. 
Hence, in order to compute $\mu_i$ using $N$ points in the d-dimensional parameter space, we require $N(d+1)$
model realizations. The SW potential parameters are considered to be uniformly distributed in a small interval
around the nominal value in which case $\mathcal{C}_i$ is given as $(u-l)^{2}/\pi^2$~\cite{Roustant:2014}; $u$
and $l$ being the upper and lower bounds of the interval respectively.

@@

For the present application, we begin with $n_1$ = 10 samples in the 7D parameter space and add 5 points
at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivatives in
Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
pertaining to the estimation of DGSM can be substantial, it is nevertheless several orders of magnitude smaller
than directly estimating the Sobol indices as mentioned earlier. 
In Figure~\ref{fig:ub}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
end of 4 iterations. It appears that $\gamma$ is significantly more important than other parameters, whereas NEMD
predictions are relatively less sensitive to $B$ and $p$. Large sensitivity towards 
$\gamma$ and $\alpha$ (cut-off radius) is in fact expected since  these two parameters impact the lattice
constant and hence the mean free path associated with the bulk thermal conductivity directly.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/ub}
\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 25(7+1)
points is plotted for each SW potential parameter.}
\label{fig:ub}
\end{center}
\end{figure}

In the following section, we exploit these observations based on DGSM to construct a reduced order surrogate.
The surrogate enables forward propagation of uncertainty in the SW potential to the bulk thermal conductivity 
estimates, and the estimation of Sobol sensitivity indices with minimal computational effort.

>>>>

As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD
are dependent on the choice of the inter-atomic potential as well as values associated with
the individual potential parameters. In the case of silicon, the Stillinger-Weber inter-atomic potential
has been used for a wide variety of 
systems~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein).
However, according to Stillinger and Weber, the set of nominal
values as provided below in Table~2 were based on a constrained search in the 7D parameter space
to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.

@@

It is noteworthy that the underlying analysis which led to these estimates of the nominal values did not
account for the presence of uncertainty due to
measurement error, noise inherent in MD predictions, inadequacies pertaining to the potential function,
and parametric uncertainties. It is therefore likely that the proposed nominal estimates could be 
improved depending upon the application. Hence, it is critical to understand the effects of uncertainty in
SW potential parameters on bulk thermal conductivity predictions using NEMD. For this purpose, a possible
approach could involve a global sensitivity analysis of NEMD predictions on the SW potential parameters 
by estimating the so-called Sobol\textquotesingle~indices~\cite{Sobol:2001}. However, obtaining converged estimates of
Sobol\textquotesingle~indices typically requires tens of thousands of model evaluations to be able to numerically approximate
multi-dimensional integrals associated with the expectation and variance operators, especially in case $\bm{\theta}$,
the vector of uncertain model inputs is high-dimensional:

\be
 \mathcal{T}_i = \frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})} 
 \ee

 \noindent where $\mathcal{T}_i$ is the Sobol\textquotesingle~total-effect index, $\mathcal{G}$ denotes the model output,
 $\mathbb{E}_{\bm{\theta}\sim i}[]$ is an expectation over all but the $i^{\mbox{th}}$ component of 
 $\bm{\theta}$, and $\mathbb{V}_{\theta_i}()$ is the variance taken over $\theta_i$. Li and Mahadevan
 recently proposed a computationally efficient method for estimating the first-order Sobol\textquotesingle~index~\cite{Li:2016}.
However, since NEMD is compute-intensive,
estimating the Sobol\textquotesingle~indices directly would be impractical in the present scenario. Hence, instead of 
estimating Sobol\textquotesingle~sensitivity
indices, we focus our attention on the upper bound of the Sobol\textquotesingle~total-effect index to determine the relative
importance of SW potential parameters. 
It is observed that for a given application, it might be possible to 
converge to the upper bound on
Sobol\textquotesingle~index with only a few iterations~($\mathcal{O}(10^{1})$)~\cite{Kucherenko:2016}. 
In that case, estimates of the upper bound could be used in lieu of the
Sobol\textquotesingle~indices to determine relative importance of the parameters and hence 
reduce the associated computational
effort by several order of magnitude. The upper bound of the
Sobol\textquotesingle~total effect index\footnote{Sobol\textquotesingle~total effect index is a measure
 of the contribution of an 
input to the variance of the model output, also accounting for the contribution coupled with other inputs.}
($\mathcal{T}_i$) can be expressed in terms of a derivative-based sensitivity measure~(DGSM), $\mu_i$, the Poincar\' e 
constant~($\mathcal{C}_i$), and the total variance of the observed
quantity~($V$)~\cite{Lamboni:2013,Roustant:2014} as follows:

@@

\noindent The derivative-based sensitivity measure, $\mu_i$ for a given parameter, $\theta_i$ is
defined as an expectation
of the derivative of the output ($G(\bm{\theta})$) with respect to that parameter:

@@

We aim to compute the derivative-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
Sobol\textquotesingle~total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
associated with each parameter and estimate the partial derivatives in Eq.~\ref{eq:mu} using finite difference. 
Hence, in order to compute $\mu_i$ using $N$ points in the d-dimensional parameter space, we require $N(d+1)$
model realizations. The SW potential parameters are considered to be uniformly distributed in a small interval
around the nominal value in which case $\mathcal{C}_i$ is given as $(u-l)^{2}/\pi^2$~\cite{Roustant:2014}; $u$
and $l$ being the upper and lower bounds of the interval respectively.

@@

For the present application, we begin with $n_1$ = 10 samples in the 7D parameter space and add 5 points
at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivatives in
Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
pertaining to the estimation of DGSM can be substantial, it is nevertheless several orders of magnitude smaller
than directly estimating the Sobol\textquotesingle~indices as mentioned earlier. 
In Figure~\ref{fig:ub}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
end of 4 iterations. It appears that $\gamma$ is significantly more important than other parameters, whereas NEMD
predictions are relatively less sensitive to $B$ and $p$. Large sensitivity towards 
$\gamma$ and $\alpha$ (cut-off radius) is in fact expected since  these two parameters impact the lattice
constant and hence the mean free path associated with the bulk thermal conductivity directly.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/ub}
\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 200
points is plotted for each SW potential parameter.}
\label{fig:ub}
\end{center}
\end{figure}

In the following section, we exploit these observations based on DGSM to construct a reduced order surrogate.
The surrogate enables forward propagation of uncertainty in the SW potential to the bulk thermal conductivity 
estimates, and the estimation of Sobol\textquotesingle~sensitivity indices with minimal computational effort.

### 2018-04-29 Paper/setup.tex
..

Non-equilibrium molecular dynamics (NEMD) simulations are performed using LAMMPS~\cite{Plimpton:2007}.
Essentially, a thermal gradient is applied by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
as shown using a schematic in Figure~\ref{fig:setup}.

@@

There NEMD simulation has three stages associated with it as illustrated below in the flow diagram. In the
first stage, the NVT ensemble equilibrates the system to a specified bulk temperature i.e. the temperature
at which thermal conductivity is to be estimated. In the second stage, the NVE ensemble equilibrates the
thermostats at their respective temperatures. It is followed by another NVE ensemble that captures the
trajectory of individual atoms and results in a steady state estimate for the thermal energy exchange between
the two thermostats.

>>>>

In this work, non-equilibrium molecular dynamics (NEMD) simulations are performed using the 
LAMMPS~\cite{Plimpton:2007} software package.
Essentially, a thermal gradient is applied by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
as shown using a schematic in Figure~\ref{fig:setup}.

@@

The NEMD simulation has three stages associated with it as illustrated below in the flow diagram. In the
first stage, the NVT ensemble equilibrates the system to a specified bulk temperature, i.e., the temperature
at which thermal conductivity is to be estimated. In the second stage, the NVE ensemble equilibrates the
thermostats at their respective temperatures. It is followed by another NVE ensemble that captures the
trajectory of individual atoms and results in a steady state estimate for the thermal energy exchange between
the two thermostats.
